\section{Appendix: audit protocol, provenance, and reproducibility}
\label{app:audit}

\todo{Fill from csc/PREREGISTRATION.md, the B3 freeze-candidate protocol, the confirmatory manifest, and
the C6 red-team note. Keep exact hashes/seeds for reproducibility.}

\subsection{Freeze-before-confirmatory protocol}
Both routes follow: development (dev seeds) $\rightarrow$ freeze (annotated git tag $+$ machine-readable
manifest with a canonical hash $+$ pinned code hashes) $\rightarrow$ a \emph{single} confirmatory on unseen
clusters run by a fail-closed runner (verifies manifest hash, code hashes, HEAD $=$ tag commit, clean tree,
and seed disjointness before executing; a scientific FAIL still preserves the artifact). Non-selection
rules: a fixed finite operating point/scenario list, a conjunction headline (no disjunction, no post-hoc
cell addition, no pooling to mask elevation), conservative denominators (non-confirm states counted as
non-fired), and a required independent red-team re-aggregation.

\subsection{Route A confirmatory provenance}
Tag \texttt{csc-confirmatory-v1} (commit \texttt{dee8958}); manifest \texttt{da2c0f4309\dots}; artifact
\texttt{csc/results/confirmatory.json} (sha256 \texttt{8b07524e\dots}); SLURM $876329$; base seed $900000$
(source $900000\text{--}900065 \rightarrow$ target $1800000\text{--}1800065$). Verdict:
\texttt{headline\_core\_pass=false} (Table~\ref{tab:routeA}).

\subsection{Route B3 confirmatory provenance and seed schedule}
Tag \texttt{csc-b3-confirmatory-v1} (commit \texttt{0595f64}); manifest hash
\texttt{a96dc0de55917c0f6dadf39807ea3cdd7539df1802f57917549ae1ddbb65cf62}; artifact
\texttt{csc/results/b3\_confirmatory\_result.json} ($+$ \texttt{.sha256}); SLURM $878107$
(cpu-high/nodecpu02). Seed schedule: cluster seed $=3000000 + 100000\cdot(\text{cell index}) +
(\text{replicate})$; target offset $10000$; $5376$ clusters; range $[3000000,14100047]$; verified disjoint
from Route-A source/target seeds ($900000\text{--}65$, $1800000\text{--}65$), development blocks, and the
smoke/test range ($<100000$). $C_6$ red-team confirmed $C_1$--$C_5$ without correction.

\subsection{Method lock (Route B3)}
\texttt{calibration\_version = p24d\_cross\_budget\_alpha\_spending\_studentized\_fixed\_margin};
$h_1$ basis $=$ pc (rank $3$), centered ($\pm\tfrac12$) condition coding, $C=0.5$; condition-matched
fixed-margin $h_0$ bootstrap ($n_{\text{boot}}=200$); studentized subject-consistency gate; family
$\alpha=0.05$, budgets $\{20,30\}$, $\alpha_{\text{budget}}=0.025$, LCB level $0.975$; $3$ folds; pair
integrity $\geq 0.95$; $\geq 8$ epochs/condition; $\geq 20$ eligible labelled paired subjects.

\subsection{Reproducibility}
\todo{Add exact commands: frozen-worktree checkout at the tag, the SLURM wrapper invocation, and the
re-aggregation script. Reference the committed result artifacts and the C6 note.}
