\section{Introduction}
\label{sec:intro}

\todo{Citations still to be added (see references.bib); prose is otherwise a full first draft, not a stub.}

Deployed machine-learning systems are increasingly asked to monitor themselves for distribution shift. Most
practical monitors watch the input or representation marginal --- they detect that $P(Z)$ has moved. But the
question that actually governs whether a deployed decision rule is still trustworthy is a statement about the
\emph{conditional}: has $P(Y\mid Z)$, the class posterior in representation space, changed? This is
\emph{concept shift}, and it is the shift that a marginal monitor cannot see by construction. In
subject-structured, high-stakes settings --- clinical EEG being our motivating example, where labels require
expert annotation and are scarce while unlabeled target recordings are plentiful --- there is a strong
temptation to certify concept shift from the unlabeled target alone, using a marginal move as a proxy for a
conditional move. This paper asks, for that setting, three questions: \emph{when can such a proxy certify
concept shift, when must it abstain, and what minimal extra information changes the answer?} We treat this as
an \emph{identifiability} problem, not a detection benchmark. \claimtag{C-motivation}

\paragraph{A non-identifiability boundary.}
Our first result is a boundary, not a method. We show (Prop.~\ref{prop:impossible}) that for \emph{any}
observed target marginal $Q_Z$ there exist two target laws with the same $Q_Z$ but different posteriors
$Q(Y\mid Z)$. Any certificate that is a function of the unlabeled target returns the same value on both, so
it cannot decide ``posterior unchanged'' versus ``concept shift.'' There is therefore no universal,
unlabeled-target concept-shift detector; the honest output must include an explicit \emph{abstention} state.
This reframes the design goal from ``build a better detector'' to ``build a certificate that knows when it is
entitled to a claim.'' \claimtag{C-impossible}

\paragraph{An audited negative.}
The natural objection is that a sufficiently engineered unlabeled-target certificate might still work in
practice. We take that objection seriously. We build a \emph{strong} source-anchored, $Z$-only certificate
--- it is not a strawman: it uses source-domain residual evidence, a support gate, bootstrap calibration,
subject-level (cluster-valid) inference, and a fail-closed abstention path. In development sweeps it
exhibited an apparent identifiable operating core. We then \emph{froze} it (a git tag, a machine-readable
manifest with a canonical hash, and a fail-closed runner) and ran a single pre-registered confirmatory on
\emph{unseen} clusters. It failed both endpoints: the false-certification rate exceeded $\alpha$ \emph{and}
the power fell below the deployment bar (Sec.~\ref{sec:routeA}). This audited negative is the empirical
counterpart of the theorem: source-free concept evidence, even after development selection, is fragile ---
exactly the failure mode an abstention-equipped certificate exists to expose. \claimtag{C-routeA-neg}

\paragraph{A minimal-information positive.}
The theorem is not only an obstruction; it is constructive, because it says precisely what is missing ---
information that ties the target's posterior to something observable. We add the minimal such information:
a \emph{paired within-subject} structure (each subject contributes two conditions, e.g.\ ON/OFF, so the
subject is its own reference and the subject random effect cancels) plus a \emph{small label audit} on
eligible paired subjects. This yields a \emph{target-internal} conditional-change certificate that never
consults a source posterior, thereby sidestepping the contaminated source-reference that broke a
few-label unpaired route. Under the identical freeze-before-confirmatory discipline, this Route~B3
certificate \emph{passed} all pre-registered criteria $C_1$--$C_6$ on unseen synthetic clusters, within a
declared operating envelope (Secs.~\ref{sec:routeB3method}--\ref{sec:routeB3conf}). \claimtag{C-routeB3-pos}

\paragraph{Why synthetic, and why this is the right environment.}
Every empirical result here is synthetic, and deliberately so. This paper is about identifiability and
certification, not clinical deployment. The synthetic environment is not a stand-in for a benchmark; it is a
controlled \emph{falsification} environment in which pure-conditional shift, support-visible covariate
shift, label-composition shift, paired-nuisance shift, and random-label controls are known by construction
--- so that a false certification can be measured, not merely suspected. Introducing real EEG before the
identifiability boundary is fixed would confound method failure with unknown ground truth. Real EEG (e.g.\
Parkinson's ON/OFF paired recordings, cross-site nulls) is the intended next validation target and requires
its own freeze and pre-registration; it is future work, not a claim of this paper (Sec.~\ref{sec:discussion}).

\paragraph{Contributions.}
\begin{enumerate}
  \item \textbf{A non-identifiability result} for unlabeled-target concept-shift certification: no $Z$-only
        certificate can decide concept shift for any observed marginal (Prop.~\ref{prop:impossible}),
        forcing an abstention state. \claimtag{C-impossible}
  \item \textbf{A fail-closed $Z$-only certificate and a frozen negative confirmatory}: a strong
        source-anchored certificate that looked promising in development but failed both endpoints under
        unseen-cluster testing (Sec.~\ref{sec:routeA}). \claimtag{C-routeA-neg}
  \item \textbf{A paired minimal-label certificate} using a target-internal within-subject reference plus a
        small label audit, which changes the statistical problem rather than the model
        (Sec.~\ref{sec:routeB3method}). \claimtag{C-routeB3-pos}
  \item \textbf{A frozen positive confirmatory} of that certificate within a scoped synthetic envelope
        ($C_1$--$C_6$ pass; primary power $1.00$; false confirmation within the pointwise control gates),
        independently red-teamed (Sec.~\ref{sec:routeB3conf}). \claimtag{C-routeB3-pos}
  \item \textbf{A claim--evidence discipline for falsifiable shift-certification research}:
        freeze-before-confirmatory with non-selection rules, conservative denominators, fail-closed
        provenance, and independent re-aggregation --- the same machinery produced both the negative and the
        positive verdict, which is why both are credible (Sec.~\ref{sec:routeB3conf}, appendix). \claimtag{C-protocol}
\end{enumerate}

\paragraph{The deployment view.}
A recurring theme is that the correct output of a deployment-time certificate is not a binary shift/no-shift
label but a \emph{fail-closed decision system} with explicit abstention, invalidity, and
information-request states. Both routes emit such states; the difference is that Route~B3, given the minimal
extra information the theorem demands, can \emph{leave} the abstention region and earn a confirmable
positive. The scope of that positive --- synthetic, paired, scoped envelope, weak on invisible
pure-conditional shift --- is stated wherever the claim appears (Sec.~\ref{sec:discussion}).
