\section{Route B3: a paired within-subject, minimal-label certificate}
\label{sec:routeB3method}

\todo{Expand each component into method prose + a small algorithm box; add the pipeline figure caption
cross-ref. All parameter values below are the frozen method lock (calibration\_version
\texttt{p24d\_cross\_budget\_alpha\_spending\_studentized\_fixed\_margin}).}

\paragraph{The missing information.}
Prop.~\ref{prop:impossible} says the target marginal is insufficient. Route B3 supplies the minimal extra
information that breaks the tie: (i) a \emph{paired within-subject reference} --- each subject contributes
two conditions (e.g.\ ON/OFF), so the subject is their \emph{own} control and the subject random effect
cancels; and (ii) a \emph{few labels} on eligible paired subjects. Critically, the reference is
\emph{target-internal}: no source posterior is used, so Route B3 sidesteps the source-reference
contamination and covariate-extrapolation failure modes that make a source-anchored certificate fragile. \claimtag{C-b3-idea}

\paragraph{Conditional-change test.}
For a subject with conditions indexed by a centered code $c\in\{-\tfrac12,+\tfrac12\}$, we compare
\[
h_0:\ [\,Z,\ c\,] \qquad\text{vs.}\qquad h_1:\ [\,Z,\ c,\ c\times Z_{\mathrm{pc}}\,]
\]
where $Z_{\mathrm{pc}}$ is a low-rank (rank $3$) principal-component basis and the $c\times Z_{\mathrm{pc}}$
interaction is the condition-dependent boundary change. The statistic is a subject-condition-vote
difference of negative log-likelihoods, $T=\mathrm{vote}(\mathrm{NLL}_{h_0})-\mathrm{vote}(\mathrm{NLL}_{h_1})$,
cross-fitted over $3$ folds. Centered ($\pm\tfrac12$) coding is essential: $0/1$ coding makes the
interaction asymmetric and induces a type-I failure. \claimtag{C-b3-test}

\paragraph{Calibrated inference (the method lock).}
The frozen certifier (\texttt{pc\_centered\_calibrated}) combines:
\begin{itemize}
  \item \textbf{Pair-integrity + eligibility guards}: pair integrity $\geq 0.95$; an eligible complete pair
        needs $\geq 8$ epochs per condition; per-condition class coverage required, else \stinv{}/\stneed{}.
  \item \textbf{Condition-matched fixed-margin $h_0$ bootstrap}: within-condition label swaps that preserve
        the per-condition class margins (Metropolis, acceptance $\propto p_0$); $n_{\text{boot}}=200$;
        invalid replicates are \emph{counted}, not dropped.
  \item \textbf{Studentized subject-consistency gate}: $Z=\overline{\Delta}_s/\mathrm{se}(\Delta_s)$ over
        per-subject deltas, requiring the lower confidence bound on $\overline{\Delta}_s$ to exceed $0$.
  \item \textbf{Cross-budget $\alpha$-spending}: family $\alpha=0.05$ split over the two positive-decision
        budgets $m\in\{20,30\}$, giving $\alpha_{\text{budget}}=0.025$ on the $p$-gates and a $0.975$ LCB.
\end{itemize}
A positive decision at budget $m$ requires the fixed-margin mean-$T$ $p\leq\alpha_{\text{budget}}$
\emph{and} the studentized $p\leq\alpha_{\text{budget}}$ \emph{and} $\mathrm{LCB}_{0.975}(\Delta_s)>0$.

\paragraph{Output states.}
Route B3 emits \stconf{} / \stnoev{} / \stneed{} / \stinv{} / \stunid{} --- there is no \stcov{} state
(covariate compatibility is not a Route-B3 claim). The design fails closed: unsound pairing, too few
epochs, or too few eligible labelled subjects yield abstention, never a confirmation. \claimtag{C-b3-states}

\begin{figure*}[t]
\centering
\begin{tikzpicture}[
  font=\small,
  node distance=6mm and 10mm,
  stage/.style={draw, rounded corners, align=center, fill=blue!5,
                text width=27mm, minimum height=13mm, inner sep=3pt},
  gate/.style={draw, diamond, aspect=2, align=center, fill=orange!12,
               inner sep=1pt, text width=17mm},
  good/.style={draw, rounded corners, align=center, fill=green!12,
               text width=26mm, minimum height=8mm, inner sep=2pt},
  abst/.style={draw, rounded corners, align=center, fill=gray!12,
               text width=26mm, minimum height=7mm, inner sep=2pt},
  flow/.style={-{Latex[length=2mm]}, thick},
]
% main left-to-right spine
\node[stage] (in) {Paired subjects\\ON/OFF $+$ few labels};
\node[gate, right=of in] (guard) {sound pair?};
\node[stage, right=14mm of guard] (test) {Conditional-change test\\$h_0:[Z,c]$ vs\\$h_1:[Z,c,c\!\times\!Z_{\mathrm{pc}}]$\\centered coding, vote $T$};
\node[stage, right=of test] (dec) {Calibrated decision\\fixed-margin $h_0$ null\\studentized gate\\cross-budget $\alpha$-spend};
% outputs
\node[good, right=of dec] (conf) {\stconf};
\node[abst, below=5mm of conf] (noev) {\stnoev};
\node[abst, below=10mm of guard] (need) {\stneed};
\node[abst, below=4mm of need] (inv) {\stinv};
% edges
\draw[flow] (in) -- (guard);
\draw[flow] (guard) -- node[above,font=\scriptsize]{yes} (test);
\draw[flow] (test) -- (dec);
\draw[flow] (dec.east) -- node[above,font=\scriptsize]{pass} (conf.west);
\draw[flow] (dec.east) to[out=-20,in=180] node[below,font=\scriptsize,pos=0.6]{fail} (noev.west);
\draw[flow] (guard.south) to[out=-90,in=90] node[right,font=\scriptsize,pos=0.3]{too few labels} (need.north);
\draw[flow] (guard.south) to[out=-110,in=110] node[left,font=\scriptsize]{bad pairing} (inv.north);
\end{tikzpicture}
\caption{Route~B3 certificate pipeline and fail-closed gates. Paired within-subject conditions plus a small
label audit pass through eligibility/pair-integrity guards; a centered ($\pm\tfrac12$) conditional-change
test produces a subject-vote statistic $T$; a calibrated decision (condition-matched fixed-margin $h_0$
bootstrap, studentized subject-consistency gate, cross-budget $\alpha$-spending) emits \stconf{} only on a
conjunctive pass. Every other path fails closed to \stnoev{}, \stneed{}, or \stinv{}; out-of-scope inputs
abstain (\stunid{}). No source posterior is used.}
\label{fig:pipeline}
\end{figure*}
