\section{Route A: a source-anchored $Z$-only certificate, and its frozen negative}
\label{sec:routeA}

Prop.~\ref{prop:impossible} is an impossibility statement about \emph{any} function of the target marginal.
Route A is its empirical counterpart: we build the strongest source-anchored $Z$-only certificate we can,
pre-register a falsifiable go/no-go, freeze it, and run it once on unseen synthetic data. It fails both endpoints. The
value of the section is that the failure is \emph{audited} --- it is what Prop.~\ref{prop:impossible} predicts
happens when a marginal certificate is asked to identify concept shift without extra information tying the
source evidence to the target posterior.

\subsection{What a $Z$-only certificate is allowed to see}
The information budget is exactly the one covered by Prop.~\ref{prop:impossible}. The certifier observes the
\emph{unlabeled} target marginal $Q_Z$ --- no target labels at all --- together with the labeled
\emph{source} data $P_S(Z,Y)$ it uses to calibrate what a shift ``looks like.'' Whatever the certifier emits
is therefore a function of $Q_Z$ (with source-derived parameters held fixed), so it is precisely the object
$f(Q_Z)$ of the proposition: two target joints $Q_0,Q_1$ with $Q_0(Z)=Q_1(Z)=Q_Z$ but different posteriors
are indistinguishable to it. Route A does not try to escape this budget; it asks whether, \emph{within} it, a
heavily engineered instrument can still be useful in practice under the extra structure of
Assumption~\ref{ass:T}.

\subsection{Certificate design (high level)}
The design is deliberately strong and source-anchored --- it is \textbf{not} a strawman thrown up to be
knocked down. It instantiates the three-state output of Sec.~\ref{sec:theory} (\stcov{} / \stsus{} / \stunid{})
from the following components. \claimtag{C-routeA-design}
\begin{itemize}
  \item A \emph{source-side concept statistic} that measures how far the target marginal has moved along the
  boundary-relevant directions the source can span.
  \item A \emph{parametric-bootstrap null} under the fitted no-shift model $h_0$: conditioning on $(Z,D)$ and
  resampling $Y^\ast$ to obtain a calibrated reference for ``no concept shift,'' rather than relying on an
  asymptotic approximation.
  \item A \emph{support gate} that abstains on disconnected or rank-deficient designs (bipartite connectivity
  via union--find, minimum cell counts, and design conditioning), so the certifier refuses when the
  source--target overlap cannot support inference.
  \item A low-moment \emph{atlas} of orthogonal covariate / concept / label subspaces, ordered by SNR, that
  fixes the mechanism family the source spans (the span invoked by Assumption~\ref{ass:T}).
  \item \emph{Direction-linked} concept evidence: a per-direction bootstrap with a global max-statistic /
  step-down procedure, so evidence is attributed to specific atlas directions rather than to an undifferentiated
  omnibus.
  \item An explicit \emph{label subspace and label gate} for the label-shift trap of Table~\ref{tab:taxonomy}
  (a change in $P(Y)$ mimicking concept movement along the class-mean subspace).
  \item \emph{Subject-level, cluster-valid} inference throughout (a subject vote), so the analysis unit matches
  the exchangeable unit and does not over-count epochs.
  \item A \emph{fail-closed}, three-state verdict: it emits \stcov{}/\stsus{} only when the gates pass and
  otherwise abstains (\stunid{}).
\end{itemize}
The estimator-level engineering (statistic construction, bootstrap wiring, and gate thresholds) is deferred to
Appendix~\ref{app:audit}; the main flow needs only that the certificate is source-anchored and genuinely
tries to extract concept evidence from $Q_Z$.

\subsection{Development suggested an identifiable core}
A pre-registered difficulty-envelope sweep (a star design over effect size, subjects, epochs, correlation,
imbalance, leakage, and mechanism family) located an apparent favourable operating point $P_{\text{baseline}}$
(concept effect $14$; $22$ subjects/domain; $30$ target subjects; balanced priors; correlation $0.2$;
covariate leakage $10$; $3$ concept domains; $22$ epochs). At this point the development map showed visible-concept
power $0.83$ (Clopper--Pearson lower bound $0.56$) with forbidden (false-certification) rate $0/12$.
Crucially, the development map \emph{itself} flagged its own limitation: $12$ clusters/cell give only a
Clopper--Pearson upper bound $\approx 0.221$ on the forbidden rate --- that is a \emph{boundary locator} for
where to run a real confirmatory, \textbf{not} error control, and it was never treated as one.
\claimtag{C-routeA-dev}

\subsection{The frozen confirmatory protocol}
We then froze the method: an annotated git tag \texttt{csc-confirmatory-v1} (commit \texttt{dee8958}), a
machine-readable manifest with canonical hash \texttt{da2c0f4309\dots}, and a fail-closed runner that verifies
the manifest hash, the pinned code hashes, that HEAD equals the tag commit, a clean tree, and seed disjointness
before executing. A \emph{single} confirmatory then ran on \emph{unseen} synthetic clusters at base seed $900000$
(source seeds $900000\text{--}900065 \rightarrow$ target seeds $1800000\text{--}1800065$, disjoint streams).
The pre-registered headline is a \emph{conjunction} of a false-certification gate and a power gate: to pass,
the certifier must both keep the forbidden rate controlled \emph{and} clear the power bar. The non-selection
rules that make this falsifiable are fixed in advance: a fixed finite point list (no post-hoc cell addition),
a conjunction headline (no disjunction, no pooling to mask elevation), maximum forbidden failures $=0$
($0$-failure CP-UB $\leq \alpha$), a power bar of $0.50$ evaluated with a $\max(\text{conditional},
\text{unconditional})$ guard so the source-invalid exclusion cannot inflate the headline, a minimum of $\geq
59$ valid clusters (else \textsc{Inconclusive}), and the frozen-code plus freshness provenance guards of
Appendix~\ref{app:audit}.

\begin{table}[t]
\centering
\caption{Route A, same operating point $P_{\text{baseline}}$, evaluated two ways. The frozen confirmatory
($\geq 59$ valid clusters; $0$-failure CP-UB $\leq 0.05$; power bar $0.50$ with a
$\max(\text{conditional},\text{unconditional})$ guard) refutes the development core:
\texttt{headline\_core\_pass=false}.}
\label{tab:routeA}
\begin{tabular}{@{}lll@{}}
\toprule
 & development (P1.5 map, dev seeds) & confirmatory (frozen, unseen seed $900000$) \\
\midrule
clusters                 & $12$/cell                 & $G=66$, $N_{\text{valid}}=65$ \\
visible-concept power     & $0.83$ (CP-LB $0.56$)     & $\mathbf{0.43}$ ($28/65$; CP-LB $\mathbf{0.326}$) \\
forbidden (false-cert)    & $0/12$                    & $\mathbf{1/65}$, CP-UB $\mathbf{0.0709} > \alpha{=}0.05$ \\
headline                  & apparent favourable core  & \textbf{FAIL both endpoints} \\
\bottomrule
\end{tabular}
\end{table}

% Route A's dev-vs-confirmatory collapse is panel (a) (left column) of the combined frozen-evidence
% figure~\ref{fig:evidence}, in Sec.~\ref{sec:routeB3conf}.

\subsection{The failure}
The confirmatory refutes the development core on both endpoints (Table~\ref{tab:routeA};
Fig.~\ref{fig:evidence}(a)). Of $G=66$ generated clusters, $N_{\text{valid}}=65$ passed the source-validity gate.
The forbidden gate fails: the certifier false-certified $1/65$ clusters, giving a Clopper--Pearson upper bound
of $0.0709 > \alpha = 0.05$ (\texttt{forbidden\_pass=false}). The power gate also fails: it fired on only
$28/65$ visible-concept clusters, for conditional power $0.4308$ (CP-LB $0.3262$) and unconditional power
$0.4242$ (CP-LB $0.3209$), against a required $41$ fired for pass. Because the headline is the conjunction of
the two gates, \texttt{headline\_core\_pass=false}. \claimtag{C-routeA-neg}

\subsection{Reading}
The negative is not a bug: it is the freeze-before-confirmatory protocol doing its job, and it is the
empirical counterpart of Prop.~\ref{prop:impossible}. Per protocol the result was committed and \emph{not}
rerun; no threshold, seed, manifest, or tag was changed after the fact, and the secondary descriptive point
$P_{\text{strong}}$ was not run. Route A therefore establishes that even a plausible, heavily engineered,
source-anchored $Z$-only certificate --- audited and frozen --- can fail both a false-certification bound and a
power bar on unseen synthetic data. This is exactly what the proposition predicts: without extra information tying source
evidence to the target posterior, marginal concept evidence is fragile. Because the failure is engineered,
audited, and frozen rather than incidental, it is not an arbitrary excuse to add machinery; it motivates
supplying a small, targeted amount of additional information in Route B3 (Sec.~\ref{sec:routeB3method}).
\claimtag{C-routeA-read}
