\section{Appendix: audit protocol, provenance, and reproducibility}
\label{app:audit}

\subsection{Freeze-before-confirmatory protocol}
Both routes follow: development (dev seeds) $\rightarrow$ freeze (annotated git tag $+$ machine-readable
manifest with a canonical hash $+$ pinned code hashes) $\rightarrow$ a \emph{single} confirmatory on unseen
clusters run by a fail-closed runner (verifies manifest hash, code hashes, HEAD $=$ tag commit, clean tree,
and seed disjointness before executing; a scientific FAIL still preserves the artifact). Non-selection
rules: a fixed finite operating point/scenario list, a conjunction headline (no disjunction, no post-hoc
cell addition, no pooling to mask elevation), conservative denominators (non-confirm states counted as
non-fired), and a required independent red-team re-aggregation.

\subsection{Route A confirmatory provenance}
Tag \texttt{csc-confirmatory-v1} (commit \texttt{dee8958}); manifest \texttt{da2c0f4309\dots}; artifact
\texttt{csc/results/confirmatory.json} (sha256 \texttt{8b07524e\dots}); SLURM $876329$; base seed $900000$
(source $900000\text{--}900065 \rightarrow$ target $1800000\text{--}1800065$). Verdict:
\texttt{headline\_core\_pass=false} (Table~\ref{tab:routeA}).

\subsection{Route B3 confirmatory provenance and seed schedule}
Tag \texttt{csc-b3-confirmatory-v1} (commit \texttt{0595f64}); manifest hash
\texttt{a96dc0de55917c0f6dadf39807ea3cdd7539df1802f57917549ae1ddbb65cf62}; artifact
\texttt{csc/results/b3\_confirmatory\_result.json} ($+$ \texttt{.sha256}); SLURM $878107$
(cpu-high/nodecpu02). Seed schedule: cluster seed $=3000000 + 100000\cdot(\text{cell index}) +
(\text{replicate})$; target offset $10000$; $5376$ clusters; range $[3000000,14100047]$; verified disjoint
from Route-A source/target seeds ($900000\text{--}65$, $1800000\text{--}65$), development blocks, and the
smoke/test range ($<100000$). $C_6$ red-team confirmed $C_1$--$C_5$ without correction.

\subsection{Method lock (Route B3)}
\texttt{calibration\_version = p24d\_cross\_budget\_alpha\_spending\_studentized\_fixed\_margin};
$h_1$ basis $=$ pc (rank $3$), centered ($\pm\tfrac12$) condition coding, $C=0.5$; condition-matched
fixed-margin $h_0$ bootstrap ($n_{\text{boot}}=200$); studentized subject-consistency gate; family
$\alpha=0.05$, budgets $\{20,30\}$, $\alpha_{\text{budget}}=0.025$, LCB level $0.975$; $3$ folds; pair
integrity $\geq 0.95$; $\geq 8$ epochs/condition; $\geq 20$ eligible labelled paired subjects.

\subsection{Class-balanced subject-condition weighting (Route B3)}
\label{app:weighting}
The per-subject loss \eqref{eq:loss} is the class-balanced form of a weighted average with weights
$w_{sce}=\bigl(|\mathcal{C}_s|\,|\mathcal{Y}|\,n_{scy}\bigr)^{-1}$ for an epoch $e$ in the $(s,c,y)$ cell,
where $n_{scy}=|E_{scy}|$. These weights form $\ell_s$ and are also the sample weights of the logistic fits
for $h_0,h_1$. Two invariances follow. (i) Each subject contributes total weight
$\sum_{c\in\mathcal{C}_s}\sum_{y\in\mathcal{Y}}\sum_{e\in E_{scy}} w_{sce}=1$, so the fit weights over a
training fold sum to the number of training \emph{subjects}, not epochs --- a subject with many epochs, or a
dominant class, gains no leverage over the boundary. (ii) The estimand is invariant to per-cell epoch
duplication: duplicating the epochs of a $(s,c,y)$ cell rescales $n_{scy}$ and leaves $\ell_s$, $T$, and the
fitted boundary unchanged up to optimizer tolerance. This is what makes the subject, not the epoch, the
exchangeable unit throughout.

\subsection{Condition coding: $0/1$ vs.\ centered (Route B3)}
\label{app:coding}
The frozen method codes the condition as $c\in\{-\tfrac12,+\tfrac12\}$ rather than $\{0,1\}$. With $0/1$
coding the interaction $c\times Z_{\mathrm{pc}}$ is supported only on the condition-$1$ rows, giving $h_1$
extra feature capacity for one condition only. Under the $\ell_2$-shrunk null $h_0$, the fixed-margin
bootstrap labels $Y^\ast$ are then systematically \emph{less} separable than the real labels, so the observed
$T$ exceeds its bootstrap reference even with no conditional change --- a type-I inflation. In development
audits the $0/1$ parameterization raw-rejected no-concept controls at rates far above $\alpha$, whereas the
centered $\pm\tfrac12$ coding --- which shrinks the condition main effect and the interaction on the same
footing --- restored calibration. The confirmatory (Sec.~\ref{sec:routeB3conf}) uses centered coding, and its
controls satisfy the pointwise gates.

\subsection{Reproducibility}
Each frozen confirmatory runs from a detached git worktree checked out at its tag, via a fail-closed SLURM
wrapper that re-verifies provenance before executing:
\begin{itemize}
  \item \textbf{Route B3:} \texttt{git worktree add --detach <dir> csc-b3-confirmatory-v1}; then
        \texttt{sbatch --chdir=<dir> csc/mininfo/run\_b3\_confirmatory.sbatch}. Output:
        \texttt{csc/results/b3\_confirmatory\_result.json} ($+$ \texttt{.sha256}); the $C_6$ re-aggregation
        independently recomputes $C_1$--$C_5$ from the per-cluster records.
  \item \textbf{Route A:} \texttt{git worktree add --detach <dir> csc-confirmatory-v1}; then
        \texttt{sbatch --chdir=<dir> csc/run\_confirmatory.sbatch}. Output:
        \texttt{csc/results/confirmatory.json}.
\end{itemize}
Both wrappers abort (infra-fail, non-zero exit) unless HEAD equals the tag commit, the tree is clean, the
manifest hash matches, and the seed streams are disjoint; a scientific FAIL still preserves and hashes the
artifact.
