\section{Route B3: a paired within-subject, minimal-label certificate}
\label{sec:routeB3method}

Proposition~\ref{prop:impossible} establishes that the target marginal $Q_Z$ (the unlabeled target
marginal of Sec.~\ref{sec:theory}) alone cannot identify a
change in the concept $P(Y\mid Z)$: a pure conditional shift is, in the worst case, indistinguishable from
a benign covariate shift when only the feature distribution is observed. A certificate that reports
\stconf{} must therefore acquire more than $Z$. Route~B3 supplies a small, targeted amount of information
that breaks this tie while keeping the acquisition auditable and fail-closed. Two design commitments carry
the section. First, the reference against which a conditional change is measured is \emph{target-internal}:
each subject appears under two experimental conditions and serves as their own control, so that no source
posterior is ever invoked. This is precisely the property that sidesteps the source-reference contamination
and covariate-extrapolation failure modes that made an earlier unpaired few-label route fragile: a
source-anchored decision boundary imported into the target extrapolates onto target-only feature regions and
silently conflates covariate movement with concept movement. Second, the extra information is a
\emph{small, targeted amount of labels} queried only on eligible paired subjects, and it enters the
procedure through a formal eligibility contract rather than through post-hoc filtering.
\claimtag{C-b3-idea}
We name the method the \emph{paired minimal-label concept certificate}; ``minimal-label'' is a method name,
not a formal optimality claim --- Proposition~\ref{prop:impossible} proves $Z$-only \emph{insufficiency}, not
that the paired-plus-few-labels design is the unique or mathematically minimal information that suffices.
All parameter values below are the frozen method lock
(calibration version \texttt{p24d\_cross\_budget\_alpha\_spending\_studentized\_fixed\_margin}); the scope of
the evidence in this paper is synthetic.

\subsection{Paired target audit setup}
\label{sec:b3-setup}
The atomic observation is a triple $(s,c,e)$: $s$ indexes a biological subject, $c$ is a \emph{centered}
condition code $c\in\{-\tfrac12,+\tfrac12\}$ encoding the subject's two experimental conditions (e.g.\ an
ON and an OFF state), and $e$ indexes an epoch (trial) recorded for that subject under that condition. Each
epoch carries a feature vector $Z_{sce}$ and, when queried, a label $Y_{sce}$. Labels are acquired at the
epoch level within a queried subject--condition unit, but the analysis never treats individual epochs as the
unit of evidence. Instead it aggregates each subject--condition cell into a \emph{subject-condition vote},
and the biological subject is the unit of inference throughout (Section~\ref{sec:b3-stat}).

The label budget is a single integer $m$: the number of \emph{eligible} paired subjects for which labels are
queried. A subject counts toward $m$ only if it satisfies the eligibility contract of
Section~\ref{sec:b3-guards}; ineligible subjects are never converted into evidence, so $m$ is a budget of
sound audit units, not of raw queries. The reference for every comparison is the subject's own other
condition: for subject $s$ the boundary implied by $c=-\tfrac12$ is contrasted against the boundary implied
by $c=+\tfrac12$, so that the subject random effect --- the dominant nuisance in cross-subject EEG --- cancels
inside the subject. No quantity in the certificate is a function of a source-domain posterior; the entire
decision is computed from the paired target batch and its queried labels.

\subsection{Eligibility and fail-closed guards}
\label{sec:b3-guards}
The guards are stated as a \emph{contract}: a set of pre-conditions that must hold \emph{before} a positive
confirmation is admissible. They are not post-hoc exclusions applied after inspecting the statistic. If any
pre-condition fails, the certificate short-circuits to an abstention state
(\stneed{} or \stinv{}) and the confirmatory branch is never entered.

\begin{itemize}
  \item \textbf{Pair integrity} $\geq 0.95$: the fraction of subjects that form a well-formed two-condition
        pair must meet this threshold, otherwise the batch is declared \stinv{}.
  \item \textbf{Complete pair}: an eligible subject must have \emph{both} conditions present; a subject
        missing one condition is not an audit unit.
  \item \textbf{Epoch sufficiency}: each present condition must carry $\geq 8$ epochs, so that the
        subject--condition vote is estimated from a non-degenerate cell.
  \item \textbf{Per-condition class coverage}: within the queried audit set, each condition must contain the
        required class support, so that the condition-wise boundary contrast is estimable. Individual
        subjects need not contain every class; the biological subject remains the exchangeable unit through
        grouped fitting and subject-level aggregation.
  \item \textbf{Budget floor} $m\geq 20$: a positive confirmation is admissible only once at least $20$
        eligible paired subjects have been queried; below the floor the output is \stneed{}.
\end{itemize}

Because the guards are pre-conditions, their correctness is itself testable: the confirmatory design includes
adversarial control conditions --- \texttt{missing\_pair} (subjects with a dropped condition) and
\texttt{unequal\_epochs\_extreme} (grossly imbalanced epoch counts across the two conditions) --- constructed
specifically to trip the contract. These controls exist to demonstrate that the guards \emph{fail closed}:
each produces $0/576$ false confirmations, i.e.\ no adversarial batch is ever certified.

\subsection{Conditional-change models}
\label{sec:b3-models}
Given the centered code $c$ and the feature $Z$, we contrast two logistic posteriors for the label $Y$:
\begin{align}
  h_0:&\quad P(Y\mid Z,c)\ \text{modeled from features}\ [\,Z,\ c\,], \label{eq:h0}\\
  h_1:&\quad P(Y\mid Z,c)\ \text{modeled from features}\ [\,Z,\ c,\ c\times Z_{\mathrm{pc}}\,],
  \label{eq:h1}
\end{align}
where $Z_{\mathrm{pc}}$ is a rank-$3$ principal-component basis of $Z$ and both models are $\ell_2$-regularized
logistic regressions with inverse-penalty $C=0.5$. Model $h_0$ allows the condition to shift the class prior
(a main effect of $c$) but forces the decision boundary in feature space to be \emph{shared} across
conditions; model $h_1$ adds the interaction term $c\times Z_{\mathrm{pc}}$, which lets the boundary
\emph{rotate} with the condition. A conditional-change (concept) shift is exactly the situation in which the
interaction improves fit beyond what the main effect explains, so the $h_0$-vs-$h_1$ comparison isolates
condition-dependent boundary movement rather than mere prior movement.

Centered ($\pm\tfrac12$) coding of $c$ is load-bearing: with $0/1$ coding the interaction $c\times Z_{\mathrm{pc}}$
has support only on the condition-$1$ rows and therefore aliases with the main effects under $\ell_2$
shrinkage, a calibration pathology, whereas centered coding symmetrizes the condition main effect and the
interaction so both are shrunk on the same footing. Development audits found the $0/1$ parameterization
anti-calibrated and the frozen method uses centered coding; the full audit is deferred to
Appendix~\ref{app:coding}.

\subsection{Subject-condition weighted cross-fitted statistic}
\label{sec:b3-stat}
The per-subject loss is class-balanced and averaged hierarchically so that no epoch, class, or condition
dominates. In simplified form, for a fitted model $h$ and subject $s$ with condition set $\mathcal{C}_s$,
\begin{equation}
  \ell_s(h)\ =\ \frac{1}{|\mathcal{C}_s|}\sum_{c\in\mathcal{C}_s}\ \frac{1}{|\mathcal{Y}|}\sum_{y\in\mathcal{Y}}\
  \frac{1}{|E_{scy}|}\sum_{e\in E_{scy}}\ \bigl[-\log h_y(Z_{sce},\,c)\bigr],
  \label{eq:loss}
\end{equation}
where $E_{scy}$ is the set of epochs of the $(s,c,y)$ cell and $h_y$ is the model's probability of the true
class $y$. Averaging over conditions, then classes, then epochs makes $\ell_s$ a class-balanced,
condition-balanced per-subject quantity; the full class-balanced weighting is given in
Appendix~\ref{app:weighting}. The
certificate statistic is the mean over subjects of the fit improvement of $h_1$ over $h_0$,
\begin{equation}
  T\ =\ \frac{1}{S}\sum_{s=1}^{S}\bigl[\,\ell_s(h_0)-\ell_s(h_1)\,\bigr],
  \label{eq:Tstat}
\end{equation}
with $S$ the number of audited subjects. Three properties are enforced. (i) The \emph{subject} is the unit
of inference: epochs never become independent samples, and $T$ is an average over $S$ subject deltas, not
over epochs. (ii) The losses in \eqref{eq:loss} are \emph{cross-fitted} over $n_{\text{folds}}=3$ folds that
are \emph{grouped by subject}, so a subject's own epochs never appear in both the fit and the evaluation
of its delta. (iii) The fit weights \emph{sum to the number of training subjects} in a fold, not to the
number of training epochs, so a subject with many epochs does not gain influence over the fitted boundary.

\subsection{Fixed-margin \texorpdfstring{$h_0$}{h0} bootstrap}
\label{sec:b3-bootstrap}
The null hypothesis is ``no conditional concept change,'' i.e.\ the shared-boundary model $h_0$ is adequate.
To calibrate $T$ under this null we resample labels from the fitted null posterior while holding fixed the
one aspect of the data that is a \emph{nuisance} rather than concept evidence: the per-condition class
composition. Concretely, we fit $h_0$ and draw bootstrap labels $Y^\ast\sim\hat{p}_0(Y\mid Z,c)$ subject to
the constraint that the per-condition class margins are preserved,
\begin{equation}
  N^\ast_{c,y}\ =\ N_{c,y}\qquad\text{for every condition }c\text{ and class }y,
  \label{eq:margins}
\end{equation}
implemented as within-condition label swaps with Metropolis acceptance proportional to $\hat{p}_0$. Fixing
$N^\ast_{c,y}=N_{c,y}$ matters because condition-wise class/prior composition is exactly the kind of
label-composition difference that $h_0$ is allowed to explain via its main effect of $c$; letting the
margins drift would leak that composition into the null distribution of $T$ and inflate apparent evidence.
We draw $n_{\text{boot}}=200$ replicates. Replicates that fail the fit (e.g.\ a degenerate resampled cell)
are \emph{counted}, not silently dropped, so that instability inflates rather than deflates the $p$-value.

\subsection{Studentized subject-consistency gate and cross-budget \texorpdfstring{$\alpha$}{alpha}-spending}
\label{sec:b3-decision}
A large mean $T$ can arise from one or two influential subjects; the certificate additionally requires that
the effect be \emph{consistent across subjects}. Let $\Delta_s=\ell_s(h_0)-\ell_s(h_1)$ be the per-subject
delta from \eqref{eq:Tstat}. We form the studentized subject statistic
\begin{equation}
  Z_{\mathrm{subj}}\ =\ \frac{\overline{\Delta}_s}{\mathrm{SE}(\Delta_s)},
  \qquad
  \overline{\Delta}_s=\frac1S\sum_s\Delta_s,
  \label{eq:studentized}
\end{equation}
and require the one-sided lower confidence bound on the mean subject delta to be strictly positive,
$\mathrm{LCB}_{0.975}(\Delta_s)>0$. The final decision at a given budget $m$ is \emph{conjunctive}, combining
four independent conditions:
\begin{equation}
  \underbrace{p^{\text{fm}}_{\bar T}\le\alpha_{\text{budget}}}_{\text{fixed-margin mean-}T}
  \ \wedge\
  \underbrace{p^{\text{stud}}\le\alpha_{\text{budget}}}_{\text{studentized}}
  \ \wedge\
  \underbrace{\mathrm{LCB}_{0.975}(\Delta_s)>0}_{\text{subject consistency}}
  \ \wedge\
  \underbrace{\text{all guards pass}}_{\text{contract}} .
  \label{eq:decision}
\end{equation}
The two $p$-values are the fixed-margin bootstrap $p$-value of the mean $T$ (Section~\ref{sec:b3-bootstrap})
and the studentized $p$-value derived from \eqref{eq:studentized}. Because a positive decision may be sought
at more than one budget, we control the family-wise error by $\alpha$-spending across the two positive-decision
budgets $m\in\{20,30\}$: the family budget $\alpha_{\text{family}}=0.05$ is split evenly, giving
$\alpha_{\text{budget}}=0.025$ per budget and correspondingly a $0.975$ level for the lower confidence bound.
\claimtag{C-b3-test}

\subsection{Output states}
\label{sec:b3-states}
Route~B3 is a deployment decision system rather than a binary test; it emits one of five states.
\begin{itemize}
  \item \stconf{} --- the conjunctive decision \eqref{eq:decision} passes at an admissible budget: there is
        consistent within-subject evidence of a conditional concept change.
  \item \stnoev{} --- the guards pass and the audit runs, but the evidence does not clear the calibrated
        thresholds: no concept evidence after the pair audit.
  \item \stneed{} --- the pair structure is sound but the eligible label budget is below the floor
        ($m<20$): more labels are required before any confirmation is admissible.
  \item \stinv{} --- the pairing contract itself fails (pair integrity below threshold, incomplete pairs,
        insufficient epochs, or missing class coverage).
  \item \stunid{} --- the input is out of the certifiable scope (the branch identified as unidentifiable in
        Proposition~\ref{prop:impossible}), and the certificate abstains.
\end{itemize}
There is deliberately \emph{no} \stcov{} state: Route~B3 makes no covariate-compatibility claim, and
therefore never asserts that a shift is benign. Every non-confirming path is an abstention, so the system
fails closed --- unsound pairing, too few epochs, or too few eligible labelled subjects yield abstention,
never a confirmation. These five states extend the $Z$-only three-state output of Sec.~\ref{sec:theory}
(\stcov{}/\stsus{}/\stunid{}): the paired audit replaces the source-anchored \stsus{} with a confirmable
\stconf{}, and adds the explicit data-adequacy states \stneed{} and \stinv{}. \claimtag{C-b3-states}

\begin{figure*}[t]
\centering
\begin{tikzpicture}[
  font=\small,
  node distance=6mm and 10mm,
  stage/.style={draw, rounded corners, align=center, fill=blue!5,
                text width=27mm, minimum height=13mm, inner sep=3pt},
  gate/.style={draw, diamond, aspect=2, align=center, fill=orange!12,
               inner sep=1pt, text width=17mm},
  good/.style={draw, rounded corners, align=center, fill=green!12,
               text width=26mm, minimum height=8mm, inner sep=2pt},
  abst/.style={draw, rounded corners, align=center, fill=gray!12,
               text width=26mm, minimum height=7mm, inner sep=2pt},
  flow/.style={-{Latex[length=2mm]}, thick},
]
% main left-to-right spine
\node[stage] (in) {Paired subjects\\ON/OFF $+$ few labels};
\node[gate, right=of in] (guard) {sound pair?};
\node[stage, right=14mm of guard] (test) {Conditional-change test\\$h_0:[Z,c]$ vs\\$h_1:[Z,c,c\!\times\!Z_{\mathrm{pc}}]$\\centered coding, vote $T$};
\node[stage, right=of test] (dec) {Calibrated decision\\fixed-margin $h_0$ null\\studentized gate\\cross-budget $\alpha$-spend};
% outputs
\node[good, right=of dec] (conf) {\stconf};
\node[abst, below=5mm of conf] (noev) {\stnoev};
\node[abst, below=10mm of guard] (need) {\stneed};
\node[abst, below=4mm of need] (inv) {\stinv};
% edges
\draw[flow] (in) -- (guard);
\draw[flow] (guard) -- node[above,font=\scriptsize]{yes} (test);
\draw[flow] (test) -- (dec);
\draw[flow] (dec.east) -- node[above,font=\scriptsize]{pass} (conf.west);
\draw[flow] (dec.east) to[out=-20,in=180] node[below,font=\scriptsize,pos=0.6]{fail} (noev.west);
\draw[flow] (guard.south) to[out=-90,in=90] node[right,font=\scriptsize,pos=0.3]{too few labels} (need.north);
\draw[flow] (guard.south) to[out=-110,in=110] node[left,font=\scriptsize]{bad pairing} (inv.north);
\end{tikzpicture}
\caption{Route~B3 certificate pipeline and fail-closed gates. Paired within-subject conditions plus a small
label audit pass through eligibility/pair-integrity guards; a centered ($\pm\tfrac12$) conditional-change
test produces a subject-vote statistic $T$; a calibrated decision (condition-matched fixed-margin $h_0$
bootstrap, studentized subject-consistency gate, cross-budget $\alpha$-spending) emits \stconf{} only on a
conjunctive pass. Every other path fails closed to \stnoev{}, \stneed{}, or \stinv{}; out-of-scope inputs
abstain (\stunid{}). No source posterior is used.}
\label{fig:pipeline}
\end{figure*}

\subsection*{Algorithm}
The complete procedure is summarized in Algorithm~1. Every step operates on the paired target batch and its
queried labels; no source data or source posterior is referenced at any point.

\begin{center}
\fbox{\begin{minipage}{0.92\textwidth}
\textbf{Algorithm 1: Paired minimal-label concept certificate.}\\[2pt]
\textbf{Input:} paired target batch $\{(s,c,e,Z_{sce})\}$; queried labels $Y_{sce}$ on eligible
subject--condition units; label budget $m$; frozen method manifest (rank-$3$ $Z_{\mathrm{pc}}$, $C=0.5$,
$n_{\text{folds}}=3$, $n_{\text{boot}}=200$, $\alpha_{\text{family}}=0.05$).\\[4pt]
\begin{enumerate}\setlength{\itemsep}{2pt}
  \item \textbf{Integrity and eligibility contract.} Check pair integrity $\geq 0.95$, complete pairs,
        $\geq 8$ epochs per condition, per-condition class coverage, and budget floor $m\geq 20$. If any
        pre-condition fails, \textbf{return} \stinv{} or \stneed{} (fail closed).
  \item \textbf{Subject-grouped folds.} Partition the eligible subjects into $n_{\text{folds}}=3$
        cross-fitting folds grouped by subject (no subject split across fit and evaluation).
  \item \textbf{Fit models with subject-condition weights.} On each fold's training subjects, fit $h_0$
        (Eq.~\ref{eq:h0}) and $h_1$ (Eq.~\ref{eq:h1}) as $\ell_2$ logistic models with centered code $c$;
        set fit weights to sum to the number of training subjects.
  \item \textbf{Cross-fitted subject deltas and $T$.} On held-out subjects compute $\ell_s(h_0)$ and
        $\ell_s(h_1)$ (Eq.~\ref{eq:loss}), the per-subject deltas $\Delta_s$, and the statistic $T$
        (Eq.~\ref{eq:Tstat}).
  \item \textbf{Fit $h_0$ null generator.} Refit $h_0$ on the audit set to obtain $\hat{p}_0(Y\mid Z,c)$.
  \item \textbf{Fixed-margin $Y^\ast$ bootstrap.} For $n_{\text{boot}}=200$ replicates, draw
        $Y^\ast\sim\hat{p}_0(Y\mid Z,c)$ preserving the per-condition margins $N^\ast_{c,y}=N_{c,y}$
        (within-condition swaps, Metropolis $\propto\hat{p}_0$); recompute $T^\ast$; count invalid
        replicates.
  \item \textbf{$p$-values.} Compute the fixed-margin mean-$T$ $p$-value $p^{\text{fm}}_{\bar T}$ and the
        studentized $p$-value $p^{\text{stud}}$ from $Z_{\mathrm{subj}}$ (Eq.~\ref{eq:studentized}).
  \item \textbf{Cross-budget $\alpha$ and consistency gates.} Set
        $\alpha_{\text{budget}}=\alpha_{\text{family}}/2=0.025$ across budgets $\{20,30\}$; evaluate the
        conjunction $p^{\text{fm}}_{\bar T}\le\alpha_{\text{budget}}$, $p^{\text{stud}}\le\alpha_{\text{budget}}$,
        $\mathrm{LCB}_{0.975}(\Delta_s)>0$, and all guards pass (Eq.~\ref{eq:decision}).
  \item \textbf{Return state.} If the conjunction holds, \textbf{return} \stconf{}; else \textbf{return}
        \stnoev{} (or \stneed{}/\stinv{}/\stunid{} per the contract). Fail closed on any failed gate.
\end{enumerate}
\end{minipage}}
\end{center}
