\documentclass[10pt,conference]{article}
% FSR manuscript skeleton (Phase 3A). Draft only; numbers are frozen from results/fsr_phase2*/.
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath,amssymb}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{xcolor}

\graphicspath{{figures/}}
\newcommand{\claim}[1]{\textsf{#1}}

\title{When Subject Leakage Becomes a Shortcut:\\ Verification, Refusal, and Scoped Repair in EEG Representations}
\author{Anonymous (FSR project draft)}
\date{Draft --- \today}

\begin{document}
\maketitle

\begin{abstract}
Subject and domain information is strongly decodable from EEG representations, and it is often assumed
that decodable leakage means the model relies on a harmful shortcut. We argue this inference is
unlicensed: probing shows what is \emph{encoded}, not what is \emph{used}. We define a six-level
functional-shortcut-reliance (FSR) ladder --- detectability, reducibility, erasability, task coupling,
functional reliance, and target consequence --- and require any shortcut claim to relate levels rather
than leap from a low one to a high one. We instantiate the ladder on real EEG. First, measured leakage
magnitude does not certify functional reliance: task-head alignment is positively associated with
reliance while recomputable leakage carries the wrong sign. Second, subject signal is erasable, yet no
eraser achieves a proven target benefit across 40 held-out-target cells, and aggressive erasure can harm
the target. Third, a direct branch-local audit of a fusion backbone shows its spatial branch is the
strongest subject-leakage and load-bearing candidate, but removing the subject subspace \emph{hurts} the
target --- so FSR \emph{refuses} to call it a harmful shortcut; it is task-entangled. Fourth, on injected
positive controls we detect, localize, and exactly attribute a known harmful shortcut, and we find a
sharp \emph{repair scope boundary}: a controlled first-moment deterministic offset is repairable by a
deployable target-unlabeled mean alignment (narrowly, construction-matched), whereas a controlled
second-moment stochastic perturbation is not repaired even by an oracle-directed covariance-shrinkage.
We characterize this as a \emph{recoverability boundary}: a deployable target-unlabeled operator inverts
only corruptions that are batch-deterministic, task-separable, and identifiable, and refuses otherwise.
FSR is a shortcut \emph{verification} framework, not a domain-generalization method: it makes explicit
what measurement licenses what control conclusion, and it bounds where repair is --- and is not ---
possible.
\end{abstract}

\input{sections/01_intro}
\input{sections/02_ladder}
\input{sections/03_setup_provenance}
\input{sections/04_measurable_not_reliance}
\input{sections/05_erasable_not_beneficial}
\input{sections/06_branch_natural_verification}
\input{sections/07_controlled_repair_scope}
\input{sections/08_recoverability}
\input{sections/09_related_work}
\input{sections/10_limitations}
\input{sections/11_conclusion}

\appendix
\input{appendix/provenance_appendix}
\input{appendix/route_ledger_appendix}

\bibliographystyle{plainnat}
\bibliography{refs}
\end{document}
