\begin{abstract}
Conditional invariance penalties are commonly used to improve EEG domain generalization, but global
penalties can remove task information, collapse representations, or optimize a leakage proxy without
improving target performance. We study a selective alternative: localize conditional domain information in
task-light EEG subspaces using score-Fisher geometry, and intervene only when deletion passes an explicit
source-risk certificate.

Synthetic controls show why certification is necessary. First-moment leakage proxies miss covariance-mediated
domain information, geometry-only task protection can still delete conditionally task-useful information, and
weak learned gates can unsafe-accept Bayes-unsafe deletions. A cross-fitted log-ratio task-risk gate reduces
this failure mode, but at moderate sample sizes the certified action is often refusal rather than deletion.

On BCI-IV-2a, the framework reveals a measurement-to-control gap. In TSMNet, subject identity is localizable
but redundantly encoded across a high-dimensional latent space: low-rank deletion preserves the task but only
dents leakage, while global LPC removes leakage only by collapsing the representation to the origin. In
EEGNet, the same diagnostic deletion reduces much more subject decodability at negligible task cost, yet target
accuracy does not improve. These results suggest that conditional domain leakage is measurable, and sometimes
removable, but neither measurement nor removal is sufficient evidence of domain-generalization benefit.
Strong linear concept-erasure controls confirm this is not an artifact of a weak eraser: an optimal
closed-form eraser removes more linearly-decodable subject information than our deletion at equal task cost,
yet leaves nonlinearly recoverable residuals. Separately, the EEGNet global-LPC sweep shows that leakage
reduction need not yield a target gain, and deploying every source-fitted eraser on the held-out target confirms
this directly --- none improves target accuracy, and the only NLL movement is matched by random removal. A capacity-controlled factorial
(three seeds) further indicates that this representation-dependence is largely mediated by latent dimension ---
SPD and convolutional latents coincide at matched low dimension --- though a residual architecture effect
persists at high dimension. Safe selective invariance should
therefore be treated as a certified intervention with refusal, not as an always-on regularizer.
\end{abstract}
