\section{Methods --- TOS-CMI as measurement $\to$ certified control}

Four layers (localize $\to$ protect $\to$ gate $\to$ refuse) plus
the evaluation protocol. The method is a \textbf{measurement-and-certification} procedure, not an
always-on regularizer.

\subsection{Problem setup and conditional leakage}
We observe a representation $Z = f(X)$ of EEG trials with task labels $Y$ and a domain (subject) variable $D$.
Conditional domain leakage is the residual dependence of $Z$ on $D$ given the task, $I(Z;D|Y)$: a representation
can be domain-invariant in aggregate yet still encode subject identity \emph{within} each class. Unlike a global
marginal penalty, we treat $I(Z;D|Y)$ as something to first \textbf{localize} in $Z$ and then \textbf{delete only if
certified safe} for the task. Throughout, the held-out target domain is never used for selection, gating,
or calibration --- only for final reporting (\S2.5).

\subsection{Score-Fisher localization}
We localize the directions of $Z$ that are domain-rich but task-light using a \textbf{conditional score-Fisher}
construction. Let $G_Y$ be the label score-Fisher matrix (outer products of $\nabla_z \log p(Y|z)$) and $G_{D|Y}$ the
conditional-domain score-Fisher matrix ($\nabla_z \log q(D|z,Y)$, formed on the class-conditional measure). Both are
estimated by cross-fitting (out-of-fold scores) under a whitening metric $M = (\Sigma_W + \epsilon \Sigma_{ref})^{-1}$. The
candidate nuisance subspace $V_D$ is read off the leading generalized eigenvectors of

\begin{equation}
G_{D|Y} v = \rho (G_Y + \eta M) v,
\end{equation}

i.e. directions that maximize conditional-domain score energy relative to task score energy (large $\rho$).
This is a \textbf{score-Fisher proxy} for conditional leakage --- second-order in the log-likelihood scores, so it
detects covariance/synergy structure that a first-moment (mean-scatter) statistic is blind to --- not the
exact conditional mutual information \claimtag{C1}. The number of retained directions nDcand is chosen by an
eigengap/$\rho$-threshold rule.

\begin{figure}[t]
\centering
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[>=Latex, node distance=10mm and 12mm, font=\small,
  box/.style={draw, rounded corners, align=center, inner sep=4pt, minimum height=9mm},
  act/.style={draw, rounded corners, align=center, inner sep=4pt, minimum height=9mm, thick},
  gate/.style={draw, diamond, aspect=2.2, align=center, inner sep=1pt}]
\node[box] (z) {frozen\\ latent $Z$};
\node[box, right=of z] (sf) {score-Fisher\\ localization};
\node[box, right=of sf] (vd) {candidate\\ subspace $V_D$};
\node[box, right=of vd] (pr) {direct-sum\\ projector $P_N$};
\node[gate, right=of pr] (g) {domain-gain\\ \& task-risk\\ gates};
\node[act, above right=6mm and 14mm of g] (del) {\textbf{certified}: delete\\ $RZ=(I-P_N)Z$};
\node[act, below right=6mm and 14mm of g] (id) {\textbf{not certified}: identity\\ (abstain) $Z$};
\draw[->] (z)--(sf); \draw[->] (sf)--(vd); \draw[->] (vd)--(pr); \draw[->] (pr)--(g);
\draw[->] (g.north) to[out=60,in=180] node[above,font=\scriptsize,pos=0.55]{safe \& useful} (del.west);
\draw[->] (g.south) to[out=-60,in=180] node[below,font=\scriptsize,pos=0.55]{cannot certify} (id.west);
\end{tikzpicture}}
\caption{TOS-CMI is a measurement-to-control framework: it first localizes conditional domain information,
then intervenes only when deletion is certified safe; otherwise the control action is the identity map. The
defining branch is \emph{certified deletion} vs.\ \emph{certified refusal / abstention} --- unlike a standard
encoder--regularizer--classifier pipeline, the framework is allowed to decline to intervene.}
\label{fig:pipeline}
\end{figure}

\subsection{Direct-sum projection and the low-rank deletion diagnostic}
Given $V_D$ we delete it with an \textbf{M-oblique direct-sum projector} $P_N$ onto $V_D$ along the task carrier, and
study the complement $RZ = (I - P_N) Z$. The projector is constructed to satisfy the direct-sum conditions

\begin{equation}
R V_D = 0 \quad (\text{the nuisance subspace is removed}) \quad \text{and} \quad R T = T \quad (\text{the task carrier is preserved}),
\end{equation}

rather than mere orthogonality. We then \textbf{measure removability} by decoding $D$ and $Y$ from $RZ$ (linear and
MLP probes) and comparing against (i) the full $Z$ and (ii) a same-k \emph{random} removal control. The deletion
is informative only if it reduces domain decode well below random-k while leaving task decode unchanged.
Crucially, \textbf{direct-sum geometry is necessary for algebraic task preservation but not sufficient for
conditional task safety} \claimtag{C2}: a domain-rich direction can still carry conditional task information, which
the geometry cannot see --- motivating the gate. In the frozen EEG diagnostics (\S4) we use the M-metric
deletion (an $M$-orthogonal projection onto $V_D$) and verify task preservation empirically with held-out
probes; the certified task-protected direct-sum variant ($RT{=}T$ by construction) is part of the framework
but is not exercised in these experiments, which are therefore diagnostic rather than certified interventions.

\subsection{Conditional task-risk gate and certified refusal}
Before deletion is permitted, we certify that removing $V_D$ does not destroy task-relevant information by
bounding the conditional task risk it carries,

\begin{equation}
\Delta_Y(k) = I(Y; P_k Z | (I - P_k) Z),
\end{equation}

the task information in the deleted subspace beyond what the complement already holds. $\Delta_Y$ is estimated by a
\textbf{cross-fitted, one-step plug-in log-ratio} estimator with a power certificate (a minimum-detectable-effect
floor); a weak nested critic is insufficient because it can \textbf{unsafe-accept} deletions whose true $\Delta_Y$ is
large (Fig.~\ref{fig:synth}B). The gate combines an upper confidence bound on $\Delta_Y$ (task safety) with a lower bound on the
domain-gain (that the subspace is genuinely domain-rich). \textbf{Certification is allowed to abstain, and
abstention is a valid control decision}: if the gate cannot certify that deletion is both safe ($\Delta_Y$ small)
and useful (domain-rich) at the available sample size, the correct action is the \textbf{identity map}, not a
weaker invariance penalty \claimtag{C3}. On synthetic controls this certified gate produces zero unsafe-accepts but
is deliberately conservative (Fig.~\ref{fig:synth}D) --- an honest negative for default-on deletion, by design.

\subsection{Frozen-feature EEG evaluation protocol}
We evaluate on BCI-IV-2a (BNCI2014\_001) \citep{brunner2008bci}, loaded via the MOABB pipeline
\citep{jayaram2018moabb}, under leave-one-subject-out (LOSO), domain = subject. For each
fold we train a backbone, \textbf{freeze} it, and dump its penultimate latent $Z$ on the source subjects; all
diagnostics (\S2.2--2.4) run on the frozen $Z$, and the held-out subject is used only for reporting target/LOSO
accuracy. We compare two representations to test generality: TSMNet \citep{kobler2022spd} (LogEig/SPD tangent
latent, $d_z=210$) and EEGNet \citep{lawhern2018eegnet} (convolutional penultimate latent, $d_z=16$). As the standard baseline for ``global'' conditional
invariance we sweep an LPC penalty (CE + $\lambda \cdot I(Z;D|Y)$) over $\lambda$, with per-epoch instrumentation (task CE,
feature norm, penalty, encoder gradient, effective rank) to diagnose \emph{how} it changes the representation
(\S4.2). The instrumentation is read-only and flag-gated (default off), with verified zero effect on
training dynamics. Probes (subject/task decode) use a 50/50 trial split with linear and MLP heads; the
random-k removal control deletes the same number of M-orthonormal directions as $V_D$.

Note (frozen-feature scope): this protocol measures whether \emph{removing} localized leakage from a fixed
representation helps; it does not retrain the encoder with a certified penalty. The end-to-end variant is
out of scope here and flagged in \S6.3.

\subsection{Linear concept-erasure controls}
To separate our measurement and certification claims from the particular eraser used by TOS-CMI, we compare
the TOS ($V_D$) deletion against standard \emph{linear concept-erasure} methods on the \emph{same} frozen
latents: the closed-form optimal eraser LEACE \citep{belrose2023leace}, adversarial RLACE
\citep{ravfogel2022rlace}, and iterative nullspace projection INLP \citep{ravfogel2020inlp}. These controls
ask whether the measurement-to-control gap is merely an artifact of a weak eraser. Each method erases the
subject variable $D$; we then report subject and task decodability (linear and MLP probes) on a held-out
split, against the same-$k$ random-removal control. We use concept erasure here as a \emph{control}, not as
a competing method --- the contribution is the measurement-to-control audit, not the eraser.

\subsection{Architecture\,$\times$\,latent-dimension factorial}
To separate representation \emph{type} from latent \emph{dimension} in the removability contrast, we sweep
the latent dimension of each backbone with the training protocol, dataset, and probes held fixed: TSMNet via
the SPD size (tangent dimension $m(m{+}1)/2$ for $m\in\{6,8,10,14,20\}$, i.e.\ $d_z\in\{21,36,55,105,210\}$) and
EEGNet via the penultimate width $F_2\in\{16,32,64,128\}$ (a dimension-matched $d_z{=}210$ cell is in progress).
For each cell we re-train the backbone (ERM), freeze it, and report the nonlinear (MLP) subject-decode residual
after optimal linear erasure as the removability response, over the LOSO folds (\S4.5, Fig.~\ref{fig:capacity}).
