\section{Related work}
\label{sec:related}

\paragraph{Probing measures encoding, not use.} A probe establishes that an attribute is
\emph{decodable} from a representation, not that a model \emph{uses} it; amnesic and counterfactual
probing make the distinction operational by intervening on the representation and observing behavior,
and show that decodability and causal use can dissociate~\citep{elazar2021amnesic}. Our
L1$\leftrightarrow$L5 separation is the EEG realization of this: a subject probe measures detectability,
while head-replay $R3$ measures whether removing the subspace actually changes the task head's output.

\paragraph{Concept erasure: removed is not beneficial.} A family of methods removes a linearly-decodable
concept from a representation: LEACE erases it in closed form with provably minimal collateral
damage~\citep{belrose2023leace}; INLP removes it by iterative nullspace projection~\citep{ravfogel2020inlp};
RLACE by a relaxed adversarial minimax~\citep{ravfogel2022rlace}; and scatter/moment methods target
invariant subspaces through a generalized eigenproblem~\citep{ghifary2017sca}. These are precisely our
L3 operators. Prior work establishes \emph{removability}; we deploy the same operators source-to-target
and test the downstream consequence, finding that erasure strength does not certify a target benefit.

\paragraph{Domain generalization needs selection rigor.} Under careful model selection with a strong
ERM baseline, many invariance-based methods fail to beat ERM, and apparent gains often reflect
selection rather than a robust effect~\citep{gulrajani2021domainbed}. This is the direct warning against
reading a moving invariance proxy as a generalization gain, and it motivates our refusal to propose a
new method: we audit whether the measured proxies even predict the reliance/consequence they are assumed
to control.

\paragraph{EEG subject identity is strong and entangled.} Audits of EEG foundation models report that
subject identity is highly decodable and can confound label/cohort structure, an ``identity
trap''~\citep{lin2026identitytrap}. Because the signal is strong, equating ``decodable subject'' with
``harmful shortcut'' is tempting; our audit is designed to separate the two.

\paragraph{EEG decoders and branch structure.} The backbones we analyse are standard: filter-bank
common spatial patterns for oscillatory motor-imagery features~\citep{ang2012fbcsp}, the compact
convolutional EEGNet~\citep{lawhern2018eegnet}, and the SPD/tangent-space TSMNet with domain-specific
normalization~\citep{kobler2022tsmnet}. Branch-locality (a gated fusion over graph/temporal/spatial
branches) lets us ask whether leakage means something different in a load-bearing branch --- a question
we can pose but, for want of an instrument, not yet answer quantitatively.

\paragraph{Decompose a joint effect into pathways.} A single unlabeled adaptation number conflates a
geometry pathway and a prevalence/decision-prior pathway and admits an exact
decomposition~\citep{prior_decoupled_tta_internal}. FSR applies the same measurement-then-decompose
discipline to a different object --- leakage, erasure, task-coupling, functional reliance, and target
consequence --- rather than collapsing them into a single ``shortcut'' scalar.
