\section{Limitations}
\label{sec:limitations}

We state the limitations plainly; for an audit paper they are part of the contribution.
\begin{itemize}
\item \textbf{Provenance limit.} The pooled leakage$\to$reliance correlation is not recomputable
(per-fold leakage for two of three seeds was pruned); it is reproduced only at seed0 (sign) and carried
as \claim{FROZEN\_NOT\_RECOMPUTABLE} at pooled. Only alignment$\to$reliance is fully recomputed.
\item \textbf{Heterogeneity / small $n$.} The alignment$\to$reliance association is significant on 2a
but not on 2015; the alignment-vs-leakage contrast is at seed0, $n{=}42$, with non-significant
within-group partial betas.
\item \textbf{$\mathrm{align}_k$ is not a validated estimator}, only closer to reliance than raw
leakage.
\item \textbf{The RQ2 negative correlation is not a finding} --- it is a non-robust confound of
over-erasure and the random-$k$ anchor (Figure~\ref{fig:erasure}B); the RQ2 result is the absence of a
certified benefit (0/40).
\item \textbf{RQ4 is blocked}, not answered: per-branch leakage/reliance are unmeasured and no
checkpoint exists to measure them without retraining.
\item \textbf{Proxies, not CMI.} L1/L2 use a label-conditional linear-probe posterior-KL surrogate and
a linear-probe advantage, not an unbiased mutual information; we say ``extractable conditional domain
information,'' not ``CMI.''
\item \textbf{Erasability $\neq$ full removal} (LEACE leaves a nonlinear residual); the one
target-unlabeled positive we cite (a non-CMI adaptation control) is seed0-only support, not an FSR
result.
\item \textbf{Frozen scope.} All results re-analyse frozen artifacts on specific backbones; generality
beyond them is not claimed.
\end{itemize}
