\section{Conclusion}
\label{sec:conclusion}

We have argued, and shown on frozen EEG artifacts, that a decodable subject/domain signal is not by
itself evidence of a harmful functional shortcut. Measurable leakage magnitude does not certify
functional reliance --- task-head alignment is closer to reliance, though not a validated estimator.
Subject signal is erasable, but erasure strength does not certify a target benefit: no eraser achieves
a proven gain across 40 held-out-target cells, and aggressive erasure can harm the target. Branch load
matters --- a fusion backbone's spatial branch is load-bearing --- but branch-local leakage and
reliance are unmeasured, and the instrument to measure them does not currently exist.

\begin{center}
\emph{Measurable is not reliance. Erasable is not beneficial. Branch load matters, but branch-local
shortcut claims require missing instruments.}
\end{center}

The contribution is an audit framework, not a new domain-generalization method: the FSR ladder makes
explicit what measurement is required to support what control conclusion, and the two boundary findings
plus one honestly-blocked question show current observables do not certify shortcut reliance.
Tables~\ref{tab:claims}--\ref{tab:routes} record every claim's status and every route's inclusion, so
the boundary between what the evidence supports and what it does not is auditable.

\begin{table}[t]
\centering\small
\input{tables/table1_claim_ledger}
\caption{Claim ledger. Statuses are derived from the frozen result artifacts, not hand-set.}
\label{tab:claims}
\end{table}

\begin{table}[t]
\centering\small
\input{tables/table2_route_firewall}
\caption{Route inclusion. Only routes with a predictor$+$endpoint pairing enter quantitative tests; no
target-label-fit route does.}
\label{tab:routes}
\end{table}
